Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Progress on the results section with the trained models.

Describe the different feature-subsets that we trained and why.

>>>>

Overall we trained a total of 23 models using the entire data set. One model was trained with all of the features. We then trained a set of 11 models in which we removed a single feature as well as 11 models in which we had only one feature enabled. Even though this is not as complete as a running full feature selection, it will hopefully hint at the most useful features.
